Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-08-18 ms.tex
corrected the resolving power.
added break in the line for the link since it was running into other text.

We decided to re-visit the stellar parameters by examining the high spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
There is one set of data taken on 2013-06-22 discussed in \citet{kawahara2013starspots}.
Additionally, there is one set of observations from 2015-08-28 that was taken to understand the kinematics of the system.
Both of these observations happened after the reaction wheel failure on 2015-05-11\footnote{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.

@@

The 2013 HDS data and 2015 HDS data were taken in slightly different modes.
Figure \ref{fig:prof2013vs2015} shows an example blue-chip image from 2013 and 2015.
The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm, R=50,000\footnote{https://www.subarutelescope.org/Observing/Instruments/HDS/ume/node16.html}) has a sharper PSF and and is easier to trace.
The 2013 data was taken with a wider (2 $\times$ 30 mm) slit and an image slicer, which create 3 parallel traces for \shStar.
The \texttt{iraf} tracing routines fail with the image slicer, so we use a a flat field with a narrower (0.3 mm) slit to create traces for the 2013 data with the image slicer.
For wavelength identification, a Thorium Argon reference is used.
(Note to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas.
The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
The final fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
The final rms in this wavelength solution is 0.0021 $\AA$.
After the reference spectrum is used to find a wavelength solution, the spectrum is examined near some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines}), the Mg Triplet (Figure \ref{fig:mgTriplet}) and the Ca I 6262 $\AA$ line (Figure \ref{fig:CaILine}).

@@

\subsection{Comparison to BOSZ}
The BOSZ  \citep{bohlin2017bosz} model database is calculated up to $R = 300,000$ so it can be compared to the measurements without convolving the Subaru spectra.
We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.
The models are convolved with a Gaussian that has a standard deviation $\sigma_G = 1/57700$  to obtain a resolution of 50,000.

>>>>

We decided to re-visit the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
There is one set of data taken on 2013-06-22 discussed in \citet{kawahara2013starspots}.
Additionally, there is one set of observations from 2015-08-28 that was taken to understand the kinematics of the system.
Both of these observations happened after the reaction wheel failure on 2015-05-11\footnote{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.

@@

The 2013 HDS data and 2015 HDS data were taken in slightly different modes.
Figure \ref{fig:prof2013vs2015} shows an example blue-chip images from 2013 and 2015.
The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm, R=50,000)\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/ume/node16.html} has a sharper PSF and and is easier to trace.
The 2013 data was taken with a wider (2 $\times$ 30 mm) slit and an image slicer, which create 3 parallel traces for \shStar.
The \texttt{iraf} tracing routines fail with the image slicer, so we use a a flat field with a narrower (0.3 mm) slit to create traces for the 2013 data with the image slicer.
For wavelength identification, a Thorium Argon reference is used.
(Note to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas.
The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
The final wavelength calibration fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
The final rms in this wavelength solution is 0.0021 $\AA$.
After the reference spectrum is used to find a wavelength solution, the spectrum is examined near some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines}), the Mg Triplet (Figure \ref{fig:mgTriplet}) and the Ca I 6262 $\AA$ line (Figure \ref{fig:CaILine}).

@@

\subsection{Comparison to BOSZ}
The BOSZ  \citep{bohlin2017bosz} model database is calculated up to $R = 300,000$ so it can be compared to the measurements without convolving the Subaru spectra.
We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.
The models are convolved with a Gaussian that has a standard deviation $\sigma_G = \lambda/57700$  to obtain a resolution of 50,000.
